To Airbnb?: A Question of Revenue

### 2018-10-18 papers/full_paper.Rmd
Add round 2 reviews to repo

---
title: "To Airbnb?: A Question of Revenue"
#subtitle: "(Andy Krause and Gideon Aschwanden)Rev"
#author: "Greenfield Advisors and University of Melbourne"
date: "Revised: July 22nd, 2018"
output:
  pdf_document: default
  html_document: default
header-includes: 
   - \usepackage{setspace}\doublespacing
   - \usepackage{caption}
   - \captionsetup[table]{skip=10pt}
geometry: margin=3.3cm
bibliography: abb.bib
editor_options: 
  chunk_output_type: console
---

>>>>

---
title: "To Airbnb?: A Question of Revenue"
#subtitle: "(Andy Krause and Gideon Aschwanden)Rev"
#author: "Greenfield Advisors and University of Melbourne"
date: "Revised: October 16th, 2018"
output:
  pdf_document: default
  html_document: default
header-includes: 
   - \usepackage{setspace}\doublespacing
   - \usepackage{caption}
   - \captionsetup[table]{skip=10pt}
geometry: margin=3.3cm
bibliography: abb.bib
editor_options: 
  chunk_output_type: console
---
